
Here we give a detailed explanation of the various 
subtleties which one encounters in the implementation
of the running of the Wilson Coefficients, which are 
not described nor mentioned in the original paper 
by Buras et al.

\subsection{LO vs. NLO prescription}

\begin{itemize}
\item $C_1 \,, C_2$: the $O(1)$ terms correspond to the leading order (0 and 1 for $C_1$ and $C_2$ respectively), 
while the $O(\as)$ terms are the NLO corrections.\\

\item $C_3 \ldots C_6$: in this case the $O(\as)$ terms appear already at LO, since at typical weak scales
the top quark can be integrated out and generate a tree-level graph from a QCD-penguin diagram. Hence all 
$\mt$ depedent functions, such as $B_0$, $C_0$, $D_0$ and $E_0$ have to be taken already at LO. At NLO 
the effects of the other quarks travelling in the penguin loop are summarized in the constant terms 
$-2/3$ and $-4/9$ which therefore give the $O(\as)$ NLO corrections. Note that the effects of these two constants
amount to the redefinitions of $D_0$ and $E_0$ into $\tilde D_0$ and $\tilde E_0$. \\

\item $C_7 \ldots C_{10}$: similarly to QCD-penguin diagrams also for QED penguins the top quark can be integrated out
and generate LO contributions at $O(\as)$ with $\mt$-dependent functions. The same constants given above account 
for the NLO effects.\\

\end{itemize}

Let us consider now the RG evolution matrices.

\begin{equation}
U(\mu,m)= \overbrace{U^{(0)}(\mu,m)}^\text{LO} + 
\overbrace{ {1 \over 4\pi} \Big[ \as(\mu) J U^{(0)}(\mu,m) - \as(m) U^{(0)}(\mu,m) J \Big] }^\text{NLO}
\end{equation}
 
\begin{equation}
\hR(m_1,m_2) \equiv -\frac{2\pi}{\beta_0} \; \hV \; \left(
\overbrace{\hK^{(0)}(m_1,m_2)}^\text{LO} +
\overbrace{\frac{1}{4\pi} \sum_{i=1}^{3} \hK_i^{(1)}(m_1,m_2)}^\text{NLO} \right) \hV^{-1}
\end{equation}

The quark threshold matching matrices at leading order correspond to the 
identity matrix only, while at NLO to the full formula given in the previous sections.
Note that the prescription for the $z_i$ coefficients at the charm threshold 
(recall the functions \code{Fs} and \code{Fse}) is at NLO, or in other words 
$z_i(\mc)=0$ for $i=3 \ldots 10$ at leading order.

\subsection{Apparent divergence in the $10 \times 10$ $R$ matrix}

The $10 \times 10$ case, with full QCD+QED, leads to an apparent
divergence in the matrix $K_1^{(1)}$ (off-diagonal components)

\begin{equation}
\left( \hK_1^{(1)}(m_1,m_2) \right)_{ij} =
\Bigg\lbrace
\begin{array}{ll}
\frac{M^{(1)}_{ij}}{a_i - a_j}
\left[ \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_j} -
       \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_i} \right] & i \not= j \\
M^{(1)}_{ii} \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_i}
             \ln\frac{\as(m_1)}{\as(m_2)}             & i=j
\end{array} 
\end{equation}

due to the presence of two couples of identical eigenvalues of $\gs$. 
However one can easily verify that the divergence cancels 
by substituting $a^i = a^j + \varepsilon$ in both numerator and denominator, 
and by expanding around $\varepsilon =0$
\begin{equation}
\frac{x^{a_j} - x^{a_i}}{a_i - a_j} = x^{a_j} \frac{1 - x^\varepsilon}{\varepsilon} 
 = x^{a_j} \frac{1 - (1 + \varepsilon \log x + O(\varepsilon^2))}{\varepsilon} = 
- x^{a_j} \log x
\end{equation}
In fact, the same type of calculation leads to the diagonal element of $K_1^{(1)}$,
which can be re-expressed as
\begin{equation}
\left( \hK_1^{(1)}(m_1,m_2) \right)_{ij} =
\Bigg\lbrace
\begin{array}{ll}
\frac{M^{(1)}_{ij}}{a_i - a_j}
\left[ \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_j} -
       \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_i} \right] & \mathbf{a_i \not= a_j} \\
M^{(1)}_{ii} \left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_i}
             \ln\frac{\as(m_1)}{\as(m_2)}             & \mathbf{ a_i=a_j}
\end{array} 
\end{equation}


\subsection{Apparent divergence in the $N_f=3$ case}

The divergence appearing in the limit $N_f=3$ looks similar to the case above, since
it arises from the fact that two eigenvalues differ exactly by 1 and therefore
the combination $a_i -a_j -1$, present in various denominators, vanishes.

By performing the same type of expansions described above one can check that for pure QCD
such a divergence cancels in the combination
\[ \as(\mu) J U^{(0)}(\mu,m) - \as(m) U^{(0)}(\mu,m) J \]
while in the QED part it cancels automatically inside the matrix $K^{(0)}$
\begin{equation}
(\hK^{(0)}(m_1,m_2))_{ij} = \frac{\hM^{(0)}_{ij}}{a_i - a_j - 1}
\left[
\left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_j} \frac{1}{\as(m_1)} -
\left( \frac{\as(m_2)}{\as(m_1)} \right)^{a_i} \frac{1}{\as(m_2)}
\right] 
\label{eq:K0}
\end{equation}
and in the difference
\begin{equation}
K_1^{(1)} - \as(m_2) \; \hK^{(0)} \; H + \,\as(m_1) \; H \; \hK^{(0)}
\end{equation}

In the code we implemented the substitution $N_f \to N_f + \varepsilon$ both in the 
$U_0$ and $J$ matrices and the limit $\varepsilon \to 0$ is taken by calling the functions 
\code{U} and \code{R}, or alternatively \code{FullU}. 
Only in the definition of $K^{(0)}$ we hard-coded the solution to the entire expansion

